Google - Isolated Sign Language Recognition

### 2023-03-05 cvpr_final_report/PaperForReview.tex
Change expression way

\author{王浩 \\
國立成功大學　資訊工程學系\\
F74082141\\
{\tt\small Howard.H.Wang.23@gmail.com}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
杜孟聰\\
國立成功大學　資訊工程學系\\
F74082028\\
{\tt\small secondauthor@i2.org}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   In this paper, we classify isolated American Sign Language (ASL) signs. We create a deep learning model trained on labeled landmark data extracted using the MediaPipe Holistic Solution.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
Around $90\%$ of which are born to hearing parents many of which may not know American Sign Language. 
Without sign language, deaf babies are at risk of Language Deprivation Syndrome. 
Learning American Sign Language takes time and resources, which many parents don't have.
Training a sign language recognizer can improve the learning and confidence of parents who want to learn sign language to communicate with their loved ones.

@@

We will use the raw data extracted from MediaPipe Holistic Solution which record every movement in video by landmark.
Based on that data, we use ensamble model training a deep learning model for classifying isolated American Sign Language (ASL) signs.

%-------------------------------------------------------------------------
\subsection{Data Type}

MediaPipe Holistic Solution is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams~\cite{https://doi.org/10.48550/arxiv.1906.08172}. 
The way that MediaPipe Holistic Solution record human of facial expressions, body language, and hand movements is landmarks.
Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
These dots help a computer to understand where these important areas are and how they are moving.

@@

%------------------------------------------------------------------------
\section{Expected Result}
We hope creating the state-of-the-art model to predicted the American Sign Language (ASL) signs correctly
with the input data of every video frame landmarks captured by MediaPipe Holistic Solution.

>>>>

\author{王浩 \\
國立成功大學　資訊工程學系\\
F74082141\\
{\tt\small Howard.H.Wang.23@gmail.com}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
杜孟聰\\
國立成功大學　資訊工程學系\\
F74082028\\
{\tt\small F74082028@gs.ncku.edu.tw}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   This paper aims to classify isolated American Sign Language (ASL) signs using a deep learning model. 
   To achieve this, we trained the model on labeled landmark data extracted via the MediaPipe Holistic Solution. 
   Our approach leverages the accuracy and reliability of this technology to enhance the robustness of the model and improve its performance. 
   By accurately classifying ASL signs, our method has the potential to support individuals with hearing impairments and 
   enable better communication between hearing and non-hearing populations.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
Deaf children born to hearing parents are at risk of Language Deprivation Syndrome if they don't have access to a fully developed language early in life. 
However, learning American Sign Language (ASL) can be time-consuming and resource-intensive for parents. 
Automatic sign language recognition technology can help overcome this barrier by recognizing and translating signs into text or speech.

In this paper, we propose a novel approach to isolated sign language recognition using computer vision techniques and machine learning algorithms. 
Our approach improves accuracy, robustness, and speed, as demonstrated on a publicly available dataset.

@@

We will use the raw data extracted from the MediaPipe Holistic Solution, which records every movement in video by landmark.
Based on that data, we use an ensamble model to train a deep learning model for classifying isolated American Sign Language (ASL) signs.

%-------------------------------------------------------------------------
\subsection{Data Type}
MediaPipe Holistic Solution~\cite{https://doi.org/10.48550/arxiv.1906.08172} is a powerful, easy-to-use software tool that can detect and track multiple human body parts and gestures in real-time video streams. 
\includegraphics[width=80mm]{holistic_pipeline_example}
The way that MediaPipe Holistic Solution records facial expressions, body language, and hand movements is by using landmarks.

Landmarks or keypoints are like dots that are placed on important areas of an object or a person's body. 
These dots help a computer to understand where these important areas are and how they are moving.

@@

Our proposed model leverages a simple linear architecture with added activation functions to form 
the foundation of our approach. To enhance the model's performance, we will modify the input data format, 
taking into consideration the unique properties of facial expressions, body language, and hand movements.
\includegraphics[width=80mm]{ConvLSTM}
In addition, we will explore the use of time-series models and convolution-based models, 
such as ConvLSTM~\cite{NIPS2015_07563a3f}, to identify the optimal model for fitting the features present in our video-captured frame data. 
By evaluating multiple model architectures and comparing their effectiveness, 
we aim to select the most robust and efficient approach for our isolated American Sign Language (ASL) sign recognition task.

Our model development process is designed to enhance the accuracy and reliability of our approach, 
thereby improving the overall quality of our results. 
Through a comprehensive evaluation of various model architectures, we aim to establish a state-of-the-art ASL sign recognition system 
that can effectively support communication between deaf and hearing populations.

%------------------------------------------------------------------------
\section{Expected Result}
Our proposed state-of-the-art model, which utilizes the input data of every video frame's landmarks captured by the MediaPipe Holistic Solution, 
is expected to significantly improve the accuracy and speed of isolated sign language recognition. 
We anticipate that the model will achieve high recognition rates for individual signs, 
thus aiding in the communication and language acquisition process of individuals who are deaf or hard of hearing. 
We believe that our research will contribute to the development of more sophisticated and efficient sign language recognition technology, 
making communication more accessible for the Deaf community
